Improving legitimacy and efficiency \\ of decisions in democratic communities

### 2017-09-19 statistical-quorum.tex
Surveys evaluation.

We evaluate statistical quorum in two ways. First, we evaluate it theoretically and explore its mathematical properties.
Then we evaluate it through real-world use of the PeerMind application by a 140 members community.

@@

\subsection{Theory}

\subsection{Use in Existing Democratic Community}

@@

>>>>

We evaluate statistical quorum in two ways. First, we analyze it theoretically and explore its mathematical properties.
Then we evaluate it through real-world use of the PeerMind application by a 140 members community.

\subsection{Analysis}

\subsection{Survey}

In Figure~\ref{fig:survey-comparison} we see questions and results of the survey we made at the end of each semester.

We can see that in fall members were more satisfied with the decision making in the community and only how understandable
is the whole process received a decrease. We attribute this to the fact that the use of the web application is
a novelty and requires more effort in educating members than a traditional decision making. Moreover, decision
making in person allows one to observe others how they are participating and learn from them.

@@

\subsection{Usage comparison}

@@

\subsection{Interviews}
